WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-29 method/sec_5-data_preprocess.tex
4.2 Done

The data imported via import modules may have incorrect data, missing data, and incompatible data which cannot directly feed into simulation modules.
Thus, we need to preprocess imported data before using it for forecasting. The WDIAS supports data preprocessing capabilities via the extension modules. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/weather_data_preprocessing.pdf}
    \caption{A generic mathematical function model for weather data preprocessing}
    \label{fi:weather_data_preprocessing}
\end{figure}

@@

\subsection{Interpolation}
The interpolation module generates data at desired locations or at desired data points using a serial The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique. It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.

\paragraph{Serial Interpolation}-- During serial interpolation, we use interpolation to fill any gaps in a timeseries. The interpolation module will only consider a single timeseries, which is itself in filling these gaps.

@@

\paragraph{Spatial Interpolation}-- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

\subsection{Transformation}
Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/transformation.pdf}
    \caption{Time interval aggregration.}
    \label{fi:transformation}
\end{figure}

@@

\begin{lstlisting}[language=Python]
{
    "extensionId": "",
    "extension": "Interpolation/Transformation/Validation",
    "function": "",
    "variables": [
        {
            "variableId": "",
            "metadata/metadtaIds": {
            }
        }
    ],
    "inputVariables": [],
    "outputVariables": [],
    "trigger": [
        {
            "trigger_type": "OnChange/OnTime",
            "trigger_on": []
        }
    ],
    "options": {
    }
}
\end{lstlisting}
\begin{itemize}
    \item extensionId -- An unique identifier for new extension trigger. Should be unique among all extensions.
    \item extension -- The main extension category which is responsible for handling the extension with extracting data required and storing the output. Interpolation/Transformation/Validation support for the moment.
    \item function -- Name of the microservice which is handling the input to output mapping. \texttt{Fn()} function in the \cref{fi:weather_data_preprocessing}.
    \item variables -- Array timeseries mapping to variables. Multiple variables can be define with metadata or metadataIds of timeseries. Can be use same variable on inputVariables and outputVariables below.
    \item inputVariables -- Timeseries that need to be provide into the function
    \item outputVariables -- Timeseries that output from the function
    \item trigger -- Type of trigger for the extension. Should be one of OnTime or OnChange.
    \begin{itemize}
        \item trigger -- OnChange
        \item trigger\_on -- List of timeseries to listen on change and trigger the extension
    \end{itemize}
    \begin{itemize}
        \item trigger -- OnTime
        \item trigger\_on -- List of schedules that need to be trigger the extension in cronjob string format
    \end{itemize}
    \item options -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
\end{itemize}

@@

Extension Handler is responsible for triggering the correct extension with timeseries metadata when there is any change in the subscribed timeseries with a list of \emph{OnChange} timeseries while creating an extension trigger.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/validation.pdf}
    \caption{Extension handler.}
    \label{fi:extension_handler}
\end{figure}

When new data is inserted into one of the adapter-scalar or adapter-vector, those microservices notify the extension-handler. Then the extension-handler checks whether there is any extension subscribed for inserted timeseries. If there is an extension needed to be triggered, then it invokes the given extension with the required data.

To improve the performance of matching triggers against a timeseries, we used two mechanisms as below. First, other than only storing extension metadata in a MySQL instance of adapter-extension, we also store extension data in a reverse lookup table called triggers while creating new extension triggers. Using this reverse lookup table, we can retrieve the extensions against a given timeseries without heavy processing and less delay. Second, we cache the resulting trigger type and timeseries data using the Redis database inside the extension-handler for fast access and avoid too many queries on the MySQL database. For the separation of service responsibilities, the extension data stored in the persistence database of the adapter-extension and exposed via an endpoint.

@@

Extension scheduler is responsible for triggering the correct extension with metadata at a given time that provided at the time of creation as OnTime cron job values to the extension trigger. To improve the performance of triggering cron jobs at given time schedules, we used a few optimization mechanisms as described below. 
Same as for extension-handler, the adapter-extension exposed an endpoint to retrieve extension metadata grouped by cronjob time. Then we create cron jobs as per the data retrieved via adapter-extension. We used a low-level programming language to simulate the cron jobs for fast processing the extensions. After getting extension triggers, the extension-handler grouped them based on cronjob time and scheduled cron jobs programmatically to trigger at given times. 
When each cron job triggers at the scheduled time, each cron job also contains the extensions to be triggered. Fetching extension triggers data, and creating cron jobs occur with a long period to avoid huge overhead on adapter-extension. When a user creates a new extension trigger, those data push into a queue in the Redis database. Then the extension-handler pulls data from the queue in regular time intervals and creates new cron jobs for mentioned cronjob time. 
As mentioned above, to avoid the expansion of the programmatic cron job list that we created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cron jobs. While doing that, we also flush the Redis queue.
The extension-handler should be run as a single process for the atomicity, to avoid triggering the same extension twice.

>>>>

The data imported via import modules may have incorrect data, missing data, and incompatible data which cannot directly feed into simulation modules.
Thus, we need to preprocess imported data before using them for weather forecasting. The WDIAS supports data preprocessing capabilities via extension modules. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/weather_data_preprocessing.pdf}
    \caption{A generic mathematical function model for weather data preprocessing}
    \label{fi:weather_data_preprocessing}
\end{figure}

@@

\subsection{Interpolation}
The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique. It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.

\paragraph{Serial Interpolation} -- During serial interpolation, we use interpolation to fill any gaps in a timeseries. The interpolation module will only consider a single timeseries, which is itself in filling these gaps.

@@

\paragraph{Spatial Interpolation} -- During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

\subsection{Transformation}
Simple arithmetic manipulation of time interval transformation and shifting the series in time specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/transformation.pdf}
    \caption{Time interval aggregration.}
    \label{fi:transformation}
\end{figure}

@@

\begin{lstlisting}[language=Python]
{
    "extensionId": "",
    "extension": "Interpolation/Transformation/Validation",
    "function": "",
    "variables": [
        {
            "variableId": "",
            "metadata/metadtaIds": {
            }
        }
    ],
    "inputVariables": [],
    "outputVariables": [],
    "trigger": [
        {
            "trigger_type": "OnChange/OnTime",
            "trigger_on": []
        }
    ],
    "options": {
    }
}
\end{lstlisting}
\begin{itemize}
    \item \emph{extensionId} -- An unique identifier for new extension trigger. Should be unique among all extensions.
    \item \emph{extension} -- The main extension category which is responsible for handling the extension with extracting data required and storing the output. Interpolation/Transformation/Validation support for the moment.
    \item \emph{function} -- Name of the microservice which is handling the input to output mapping. \texttt{Fn()} function in the \cref{fi:weather_data_preprocessing}.
    \item \emph{variables} -- Array timeseries mapping to variables. Multiple variables can be define with metadata or metadataIds of timeseries. Can be use same variable on inputVariables and outputVariables below.
    \item \emph{inputVariables} -- Timeseries that need to be provide into the function.
    \item \emph{outputVariables} -- Timeseries that output from the function.
    \item \emph{trigger} -- Type of trigger for the extension. Should be one of OnTime or OnChange.
        \begin{itemize}
            \item \emph{OnChange}: \textit{trigger\_on} --- List of timeseries to listen on change and trigger the extension
            \item \emph{OnTime}: \textit{trigger\_on} -- List of schedules that need to be trigger the extension in cronjob string format
        \end{itemize}
    \item \emph{options} -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
\end{itemize}

@@

Extension handler is responsible for triggering the correct extension with timeseries metadata when there is any change in the subscribed timeseries which are provided as a list of \emph{OnChange} timeseries while creating an extension trigger.
When new data is imported into one of the scalar adapter or vector adapter, those microservices notify the extension handler. Then the extension-handler checks whether there is any extension subscribed for imported timeseries. If there is an extension needed to be triggered, then it invokes the given extension with the required data.

To improve the performance of matching triggers against a timeseries, we used two mechanisms as below. First, other than only storing extension metadata in a MySQL instance of extension adapter, we also store extension data in a reverse lookup table called triggers while creating new extension triggers. Using this reverse lookup table, we can retrieve the extensions against a given timeseries without heavy processing and less delay. Second, we cache the resulting trigger type and timeseries metadata using the Redis database inside the extension handler for fast access and avoid too many queries on the MySQL database. For the separation of service responsibilities, the extension data stored in the persistence database of the extension adapter and exposed via an endpoint.

@@

Extension scheduler is responsible for triggering the correct extension with timeseries metadata at a given time that provided while creating an extension trigger as \emph{OnTime} cron job values. To improve the performance of triggering cron jobs at given time schedules, we used a few optimization mechanisms as described below. 
Same as for extension handler, the extension adapter exposed an endpoint to retrieve extension metadata grouped by cronjob time. Then we create cron jobs as per the data retrieved via adapter-extension. We used a low-level programming language to simulate the cron jobs for fast processing the extensions. After getting extension triggers, the extension handler grouped them based on cronjob time and scheduled cron jobs programmatically to trigger at given times. 
When each cron job triggers at the scheduled time, each cron job also contains the extensions to be triggered. Fetching extension triggers data, and creating cron jobs occur with a long period to avoid huge overhead on adapter-extension. When a user creates a new extension trigger, those data push into a queue in the Redis database. Then the extension-handler pulls data from the queue in regular time intervals and creates new cron jobs for mentioned cronjob time. 
As mentioned above, to avoid the expansion of the programmatic cron job list that we created for new extension triggers, all cronjobs fetch again after a long period and flush the previously scheduled cron jobs. While doing that, we also flush the Redis queue.
The extension-handler should be run as a single process for the atomicity, to avoid triggering the same extension twice.

### 2020-05-29 method/sec_7-summary.tex
4.2 Done

Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support geo-search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

>>>>

Throughout the \cref{ch:method}, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support geo-search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

### 2020-05-29 results/sec_1-test_plan.tex
4.2 Done

Other than the above modules, \emph{adapter modules} act as the core modules and the base of the system. Also, the \emph{query module} allows the users to query for the timeseries based on the metadata and perform geo-based queries based on the locations.

The test plan is to perform load testing on the whole system and analyze the scalability of the system while measuring the operations performed on each module. Two variables can vary while doing performance testing.
\begin{enumerate}
    \item Number of requests made to the system at a given time (Requests Per Second (RPS))
    \item Request size
\end{enumerate}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/work_load/performance_study_v4.jpg}
    \caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}}
    \label{fi:performance_study_load}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{List of Test Plans}
\label{subse:test_plan_flow}
Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals and create metadata of the timeseries
    % \item Extensions
    % \begin{itemize}
    %     \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
    %     \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
    %     \item Do with Import Timeseries with error data which will go through extensions.
    % \end{itemize}
    \item Import + Extension + Export + Timeseries Queries
    \begin{itemize}
        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data.
        \item Plan for 30 minutes of the test run with the request size of 30min data.
        \item Plan for 30 minutes of the test run with the request size of 15min data.
        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling.
        % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
    \end{itemize}
    \item Query
    \begin{itemize}
        \item Query Timeseries
        \item Plan for the 5 minutes of test run.
    \end{itemize}
\end{enumerate}

@@

During the performance analysis, we used the following metrics to measure the performance of the system.
\begin{itemize}
    \item \emph{Throughput} -- Number of requests that can be processed per unit time. 
    Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} to measure the throughput.
    \item \emph{Latency} -- Taken time to respond to the request sent to the system. 
    Normally we measure with milliseconds (ms) in the \acrshort{wdias}. During the performance analysis, we measure the minimum response time, maximum response time, the average response time, and standard deviation. The standard deviation measures the mean distance of the values to their average value. It gives an idea of the dispersion or variability of the measures to their mean value. So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value), and the mean value is significant. Other than that, we measure the response time into 90\% percentile while giving the best response time up to 90\% percentile of the responses.
    \item \emph{Resource utilization} -- Resource Utilization is calculated based on the CPU and Memory usage via the K8s metrics server. It calculates the resource utilization over a 60 seconds time window. Network usage is getting based on the actual physical machines.
    \item \emph{Auto-scaling} -- We performed the load testing with two system configurations. First, we ran the microservices with a fixed number of pods inside the K8s cluster. Then k8s are only allowed to vertically scale each microservice until a container hits the CPU and memory limits defined per container or overwhelm the physical node resources. Secondly, we ran the load testing with auto-scaling enabled only for microservices, which are using higher resources with the above system configurations. Auto-scaling spawns new copies of the same microservice when the microservice gets more load than the configured percentage, and shrink the running instances when there is a lesser load.
\end{itemize}

>>>>

Other than the above modules, \emph{adapter modules} act as the core modules and the base of the system. Also, the \emph{query module} allows the users to query for the timeseries metadata and perform geo-based queries based on the locations.

The test plan is to perform load testing on the whole system and analyze the scalability of the system while measuring the operations performed on each module. Two variables can vary while doing performance testing.
\begin{enumerate}
    \item Number of requests made to the system at a given time called as \acrfull{rps}
    \item Request size
\end{enumerate}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/work_load/performance_study_v4.jpg}
    \caption{\acrshort{wdias} load testing plan with changing the request size and \acrshort{rps}.}
    \label{fi:performance_study_load}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{List of Test Plans}
\label{subse:test_plan_flow}
Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals, create metadata of the timeseries and create random extension triggers
    % \item Extensions
    % \begin{itemize}
    %     \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
    %     \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
    %     \item Do with Import Timeseries with error data which will go through extensions.
    % \end{itemize}
    \item Import + Extension + Export + Timeseries Queries
    \begin{itemize}
        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data
        \item Plan for 30 minutes of the test run with the request size of 30min data
        \item Plan for 30 minutes of the test run with the request size of 15min data
        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling
        % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling
    \end{itemize}
    \item Query
    \begin{itemize}
        \item Query Timeseries
        \item Plan for the 5 minutes of test run
    \end{itemize}
\end{enumerate}

@@

During the performance analysis, we used the following metrics to measure the performance of the system.
\begin{itemize}
    \item \emph{Throughput} -- Number of requests that can be processed per unit time. 
    Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} to measure the throughput.
    \item \emph{Latency} -- Taken time to respond to the request sent to the system. 
    Normally we measure with milliseconds (ms) in the \acrshort{wdias}. During the performance analysis, we measure the minimum response time, maximum response time, the average response time, and standard deviation. The standard deviation measures the mean distance of the values to their average value. It gives an idea of the dispersion or variability of the measures to their mean value. So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value), and the mean value is significant. Other than that, we measure the response time into 90\% percentile while giving the best response time up to 90\% percentile of the responses.
    \item \emph{Resource utilization} -- Resource utilization is calculated based on the CPU and Memory usage via the K8s metrics server. It calculates the resource utilization over a 60 seconds time window. Network usage is getting based on the actual physical machines.
    \item \emph{Auto-scaling} -- We performed the load testing with two system configurations. First, we ran the microservices with a fixed number of pods inside the K8s cluster. Then k8s are only allowed to vertically scale each microservice until a container hits the CPU and memory limits defined per container or overwhelm the physical node resources. Secondly, we ran the load testing with auto-scaling enabled only for microservices, which are using higher resources with the above system configurations. Auto-scaling spawns new copies of the same microservice when the microservice gets more load than the configured percentage, and shrink the running instances when there is a lesser load.
\end{itemize}

### 2020-05-29 results/sec_2-workload.tex
Make geo- consistent
code listing - single space and avoid span over pages
4.2 Done

As explained in the research methodology (\cref{ch:method}), we selected six primary attributes from the timeseries metadata while implementing the system architecture. Before storing the data in \acrshort{wdias}, we need to register timeseries metadata for the timeseries, and are required to provide values for the six attributes. During the test for location attribute, we selected the locations all over the world as a generic case to include all the locations without binding to a specific area.

We used 250 locations from Google’s Countries Public Data set \cite{GoogleGoogleCounties}, and considered static throughout the testing. For each location, we created four timeseries metadata by using four different values for the moduleId key attribute. Thus, combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers. We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.

@@

We used the Apache JMeter for performing the load test since it is open source. And supports distributed load testing. As mentioned in the JMeter Best Practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time". While running the load test, JMeter iterates over the timeseries metadata CSV file and assigns a new thread to work on the test scenario with given timeseries metadata. Instead of providing the randomness at run time, we stored the timeseries metadata in random order that satisfies the percentage of 70\% scalar, 20\% vector, and 10\% grid, as mentioned in \cref{se:test_plan}.
Before running the test cases, we generated the timeseries metadata in random order and wrote them into a CSV file during the setup phase. The metadata CSV file arranges in a way that, within every ten lines, seven lines are Scalar timeseries, two lines are Vector timeseries, and 1 line is a Grid timeseries.

@@

\begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_precipitation.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_precipitation.sh prepare
    Segregate single file data into multiple files based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_precipitation.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_precipitation.sh cleanup
    Clean up extracted directories
\end{lstlisting}

@@

Similar to the scalar test data prepared, we prepared the test grid data using the real water-level output of the FLO2D 150 meter hydrology model that is used in the \acrshort{curw} The FLO2D timeseries are produced as ASCII Grid files, and each data point represents a grid file that consists of 120 rows and 139 columns. To represent missing cell values of the ASCII grid file, we used the \texttt{-9} instead of \texttt{-999} as an optimization. Even with that, each file size is around 50,337 Bytes (50 Kilobytes).

\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted directories
\end{lstlisting}

@@

As mentioned in \cref{se:test_plan}, we performed another separate test plan on the query timeseries module. Here, we used the following test steps to cover most of the timeseries metadata search queries and Geo queries supported by the \acrshort{wdias}.

>>>>

As explained in the research methodology (\cref{ch:method}), we selected six primary attributes from the timeseries metadata while implementing the system architecture. Before storing the data in \acrshort{wdias}, we need to register timeseries metadata for the timeseries, and are required to provide values for the six attributes. During the test for location attribute, we selected set of locations all over the world as a generic case to include all the locations without binding to a specific area.

We used 250 locations from Google’s countries public data set \cite{GoogleGoogleCounties}, and considered static throughout the testing. For each location, we created four timeseries metadata by using four different values for the moduleId key attribute. Thus, combining all together first, we created 1000 timeseries metadata during the performance test and then stored the timeseries data against timeseries unique identifiers. We have written automated scripts to generate these data for the performance testing, and scripts are generic enough to create more timeseries metadata by changing the configurations.

@@

We used the Apache JMeter for performing the load test since it is a widely using open source tool which supports distributed load testing. As mentioned in the JMeter Best Practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time". While running the load test, JMeter iterates over the timeseries metadata CSV file and assigns a new thread to work on the test scenario with given timeseries metadata. Instead of providing the randomness at run time, we stored the timeseries metadata in random order that satisfies the percentage of 70\% scalar, 20\% vector, and 10\% grid, as mentioned in \cref{se:test_plan}.
Before running the test cases, we generated the timeseries metadata in random order and wrote them into a CSV file during the setup phase. The metadata CSV file arranges in a way that, within every ten lines, seven lines are scalar timeseries, two lines are vector timeseries, and 1 line is a grid timeseries.

@@

\begin{minipage}{\linewidth}
\begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_precipitation.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_precipitation.sh prepare
    Segregate single file data into multiple files based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_precipitation.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_precipitation.sh cleanup
    Clean up extracted directories
\end{lstlisting}
\end{minipage}

@@

Similar to the scalar test data prepared, we prepared the test grid data using the real water-level output of the FLO2D 150 meter hydrology model that is used in the \acrshort{curw}. The FLO2D timeseries are produced as ASCII Grid files, and each data point represents a grid file that consists of 120 rows and 139 columns. To represent missing cell values of the ASCII grid file, we used the \texttt{-9} instead of \texttt{-999} as an optimization. Even with that, each file size is around 50,337 Bytes (50 Kilobytes).

\begin{minipage}{\linewidth}
\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted directories
\end{lstlisting}
\end{minipage}

@@

As mentioned in \cref{se:test_plan}, we performed another separate test plan on the query timeseries module. Here, we used the following test steps to cover most of the timeseries metadata search queries and geo-queries supported by the \acrshort{wdias}.
